|

### 2019-07-05 inst/manuscript/manuscript.Rmd
Add abbreviations
Also:
 - Fix typo in table 1

@@

@@

# add proper protein functions to table 1
# also add vesicle depleted supernatant info and 
# group proteins according to localisation
marker_longlist2 <- marker_longlist %>% 
  mutate(Function = function_desc1, 
         pack_row = c(4, rep(1, 3), rep(4, 2), 1, 2, rep(1, 6), 3, rep(4, 2),
                      1, rep(2, 3), 1, rep(4, 2), 1, rep(4, 3), 1, 3, 
                      rep(1, 3), 4, 1, 2, 1, 2, 4)) %>% 
  arrange(pack_row) %>% 
  mutate(VDS = c(rep("", 11), "Y", rep("", 7), "Y", rep("", 7), 
                 rep("Y", 7), "", rep("Y", 4)))

>>>>

A1 - ATCC10231

A9 - ATCC90028

DAY B - DAY286 biofilm

DAY Y - DAY286 yeast

@@

Evp1 - extracellular vesicle protein 1 (orf19.6741)

Log<sub>2</sub>(FC) - log<sub>2</sub> fold change

MCC - membrane compartment of Can1

MDS - multidimensional scaling

MISEV - minimal information for studies of EVs

sEVs - small EVs

SP - signal peptide

TEMs - tetraspanin enriched microdomains

TM - transmembrane domain

VDM - vesicle depleted medium

WCL - whole cell lysate

@@

# add proper protein functions to table 1
# also add vesicle depleted supernatant info and 
# group proteins according to localisation
marker_longlist2 <- marker_longlist %>% 
  mutate(Function = function_desc1, 
         pack_row = c(4, rep(1, 3), rep(4, 2), 1, 2, rep(1, 6), 3, rep(4, 2),
                      1, rep(2, 3), 1, rep(4, 2), 1, rep(4, 3), 1, 3, 
                      rep(1, 3), 4, 1, 2, 1, 2, 4)) %>% 
  arrange(pack_row) %>% 
  mutate(VDM = c(rep("", 11), "Y", rep("", 7), "Y", rep("", 7), 
                 rep("Y", 7), "", rep("Y", 4)))
